Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-19 documents/BrazilSlides/slides.tex
Added some slides to the beginning, will finish slides while traveling

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Report the discovery of such inequalities
        \item Explain how these inequalities were obtained
        \item Symmetric inequalities
        \item Greater violations
        \item Different kinds of non-locality?
    \end{enumerate}
    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
    \note[item]{Talk about how symmetries play two roles in the search for quantum non-locality}
    \note[item]{Demonstrate how these inequalities are robust to noise}
    \note[item]{Finding maximally violating distributions}
\end{frame}

@@

% \begin{frame}
%     \frametitle{Notation}
%     \begin{itemize}
%         \item A subset of $V \subset \jointvar$ is a \term{marginal context}
%         \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
%         \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
%     \end{itemize}
% \end{frame}

\begin{frame}
    \frametitle{Notation}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        % \item Marginal scenario forms a \textit{simplicial complex}
        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
    \note[item]{Marginal scenario refers to the those sets of random variables}
    \note[item]{The complete set of random variables are the joint random variables}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}
    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item Convex hull, Polytope projection, Fourier-Motzkin
                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique}
    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma}
    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
    \begin{enumerate}
        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
        \item Construct \term{inflated causal parameters}
        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{itemize}
        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $N \sim N'$
        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
        \begin{align*}
            \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : N \sim N'} \\
            \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : N \sim N'} \\
        \end{align*}
        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $N \sim N'$
        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $N \sim N'$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd}
    \begin{lemma}
        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}
    \begin{corollary}
        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
    \end{corollary}
\end{frame}

\begin{frame}
    \frametitle{$d$-Separation Polynomial}
    \begin{itemize}
        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
        \item \textbf{Linear inequality} for $\graph'$
    \end{itemize}
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            \pgfmathsetmacro{\hs}{1.8};
            \pgfmathsetmacro{\vs}{1};
            \pgfmathsetmacro{\cross}{0.3};
            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
            \draw (0, 0) node[](b){??};
            \draw[thick, ] (a) -- (ab);
            \draw[thick, ] (c) -- (cd);
            \draw[thick, ] (a) -- (ac);
            \draw[thick, ->] (ac) -- (c);
            \draw[thick, ->] (ab) -- (b);
            \draw[thick, ->] (cd) -- (d);
            \draw[very thick, red]
            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
            ;
        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item \textbf{Polynomial inequality} for $\graph$!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets}
    \begin{itemize}
        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
        \item A \term{pre-injectable set} $N'$:
        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Course Graining CHSH [Optional]}
    \begin{gather*}
    \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation coarse graining $\bc{0,1,2,3} \to \bc{\br{0,3}, \br{1,2}}$
    \end{itemize}
    \[ \ba{AB | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{AB | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \[ \ba{AB|C=0} + \ba{AB|C=1} + \ba{AB|C=2} - \ba{AB|C=3} = 2\sqrt{2} \not \leq 2 \]
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}

@@

>>>>

\begin{frame}
    \frametitle{This Talk}
    \begin{enumerate}
        \item Inflation technique provides polynomial inequalities
        \item Inequalities witnessing non-local quantum correlations in the Triangle Scenario
        \item Discuss search for new non-local quantum correlations
    \end{enumerate}
    \note[item]{This talk is going to have three components}
    \note[item]{Demonstrating how something called the inflation technique allows one derive polynomial compatibility constraints for and causal structure}
    \note[item]{Using the inflation technique to find inequalities that demonstrate non-local quantum distributions on the Triangle scenario}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility}
    \vfill
    \begin{center}
        Triangle Scenario
    \end{center}
    \[ \prob[ABC] = \int_{XYZ}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    \vfill
    \begin{center}
        \noindent\rule{8cm}{0.4pt}
    \end{center}
    \vfill
    \begin{center}
        General Setting
    \end{center}
    \[ \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes] \qquad \prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}] \]
    \vfill
\end{frame}

\begin{frame}
    \frametitle{Demonstrating Inflation Technique}
    \vfill
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_1}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_1}}
    \end{columns}
    \end{center}
    \only<1>{\[\forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n}\]}%
    \only<2>{\[\AnSub[\graph]{A} \sim \AnSub[\graph']{A_1}\]}%
    \only<3>{\[\AnSub[\graph]{C} \sim \AnSub[\graph']{C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Injectable Sets}
    \begin{center}
    \begin{columns}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario_anim_2}}
        \column{0.5\linewidth}%
        \scalebox{1.0}{\input{../../figures/causal_structures/inflated_triangle_scenario_spiral_anim_2}}
    \end{columns}
    \end{center}
    \only<1>{\[\AnSub[\graph]{A,C} \sim \AnSub[\graph']{A_2,C_1}\]}%
    \only<2>{\[?? \not \sim \AnSub[\graph']{B_1,B_2}\]}%
    \only<3>{\[?? \not \sim \AnSub[\graph']{B_2,C_2}\]}%
\end{frame}

\begin{frame}
    \frametitle{Injectable Sets Defined}
    The \term{injectable sets in $\graph'$}:
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    The \term{images of the injectable sets in $\graph$}:
    \begin{align*}
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
\end{frame}

\begin{frame}
    \frametitle{Perfect Correlation Is Incompatible}

@@

@@

\begin{frame}
    \frametitle{Fritz Distribution}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/fritz_dist_plot_bits_brazil.pdf}
    \end{center}
    \[ \probplotvalue{253, 253, 84} = \f{1}{32}\br{2 - \sqrt{2}} \qquad \probplotvalue{11, 1, 0} = \f{1}{32}\br{2 + \sqrt{2}}\]
\end{frame}

\begin{frame}
    \frametitle{Fritz Distribution Violating CHSH}
    % \begin{gather*}
    % \prob[F][00\textcolor{blue}{0}] = \prob[F][11\textcolor{blue}{0}] = \prob[F][30\textcolor{blue}{1}] = \prob[F][21\textcolor{blue}{1}] = \prob[F][12\textcolor{blue}{2}] = \prob[F][03\textcolor{blue}{2}] = \prob[F][23\textcolor{blue}{3}] = \prob[F][32\textcolor{blue}{3}] = \f{1}{32}\br{2 + \sqrt{2}} \\
    % \prob[F][01\textcolor{blue}{0}] = \prob[F][10\textcolor{blue}{0}] = \prob[F][31\textcolor{blue}{1}] = \prob[F][20\textcolor{blue}{1}] = \prob[F][13\textcolor{blue}{2}] = \prob[F][02\textcolor{blue}{2}] = \prob[F][22\textcolor{blue}{3}] = \prob[F][33\textcolor{blue}{3}] = \f{1}{32}\br{2 - \sqrt{2}}
    % \end{gather*}
    \begin{itemize}
        \item $C$'s outcome acts as measurement ``setting'' for A, B; independent of $\rho_{AB}$
        \item Correlation between right bits
    \end{itemize}
    \[ \ba{A_rB_r} = \prob[A_rB_r][00] + \prob[A_rB_r][11] - \prob[A_rB_r][01] - \prob[A_rB_r][10] \]
    \[ \ba{A_rB_r | C = 0, 1, 2} = \f{1}{\sqrt{2}} \quad \ba{A_rB_r | C = 3} = - \f{1}{\sqrt{2}} \]
    \begin{itemize}
        \item Gives CHSH violation
    \end{itemize}
    \begin{align*}
    &\ba{A_rB_r|C=0} + \ba{A_rB_r|C=1} + \ba{A_rB_r|C=2} - \ba{A_rB_r|C=3} \\
    &\quad = 3 \br{\f{1}{\sqrt{2}}} - \br{-\f{1}{\sqrt{2}}} \\
    &\quad = 2\sqrt{2} \not \leq 2
    \end{align*}
\end{frame}

@@

\begin{frame}
    \frametitle{Notation [Optional]}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        % \item Marginal scenario forms a \textit{simplicial complex}
        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
    \note[item]{Marginal scenario refers to the those sets of random variables}
    \note[item]{The complete set of random variables are the joint random variables}
\end{frame}

\begin{frame}
    \frametitle{Causal Compatibility [Optional]}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}
    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities [Optional]}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item Convex hull, Polytope projection, Fourier-Motzkin
                \item Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
        \item \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique [Optional]}
    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma [Optional]}
    If one has obtained $\graph$, inflation $\graph'$ and \textit{compatible} marginal distribution $\prob[N]$ where $N \subseteq \nodes$, then:
    \begin{enumerate}
        \item There exists causal parameters $\bc{\prob[n\mid\Pa[\graph]{n}] \mid n \in \nodes}$ such that
        \[ \prob[N] = \prod_{n \in N}\prob[n\mid\Pa[\graph]{n}] \]
        \item $\AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \implies \Pa[\graph']{n'} \sim \Pa[\graph]{n}$
        \item Construct \term{inflated causal parameters}
        \[ \forall n' \in \nodes' : \prob[n'\mid\Pa[\graph']{n'}] \defined \prob[n\mid\Pa[\graph]{n}]\]
        \item Obtain \textit{compatible} marginal distributions over any $N' \subseteq \nodes'$
        \[ \prob[N'] = \prod_{n' \in N'}\prob[n'\mid\Pa[\graph']{n'}] \]
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd [Optional]}
    \begin{itemize}
        \item Inflation procedure holds for any $N \in \nodes, N' \in \nodes'$ where $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
        \item Define \term{injectable sets of $\graph'$} and \term{images of the injectable of $\graph$}
    \end{itemize}
    \begin{align*}
        \Inj[\graph]{\graph'} &\defined \bc{N' \subseteq \nodes' \mid \exists N \subseteq \nodes : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}} \\
        \ImInj[\graph]{\graph'} &\defined \bc{N \subseteq \nodes \mid \exists N' \subseteq \nodes' : \AnSub[\graph]{N} \sim \AnSub[\graph']{N'}}
    \end{align*}
    \begin{itemize}
        \item For $N' \in \Inj[\graph]{\graph'}$ there is a \textit{unique} $N \subseteq \nodes$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
        \item For $N \in \Inj[\graph]{\graph}$ there can \textit{exist many} $N' \subseteq \nodes'$ such that $\AnSub[\graph]{N} \sim \AnSub[\graph']{N'}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Inflation Lemma Cont'd [Optional]}
    \begin{lemma}
        \term{The Inflation Lemma:}~\cite[lemma 3]{Inflation} Given a particular inflation $\graph'$ of $\graph$, if a marginal model $\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}$ is compatible with $\graph$ then all marginal models $\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}$ are compatible with $\graph'$ provided that $\prob[N] = \prob[N']$ for all instances where $N \sim N'$.
    \end{lemma}
    \begin{corollary}
        Any causal compatibility inequality $I'$ constraining the injectable sets $\Inj[\graph]{\graph'}$ can be \term{deflated} into a causal compatibility inequality $I$ constraining the images of the injectable sets $\ImInj[\graph]{\graph'}$.
    \end{corollary}
\end{frame}

\begin{frame}
    \frametitle{$d$-Separation Polynomial [Optional]}
    \begin{itemize}
        \item Deflation only holds when inequality constrains probabilities $\prob[N'], N' \in \Inj[\graph]{\graph'}$
        \item \textbf{Linear inequality} for $\graph'$
    \end{itemize}
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            \pgfmathsetmacro{\hs}{1.8};
            \pgfmathsetmacro{\vs}{1};
            \pgfmathsetmacro{\cross}{0.3};
            \draw (0*\hs, 4*\vs) node[](a){$\prob[N']$};
            \draw (0*\hs, 2*\vs) node[](ab){$N' \not \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 4*\vs) node[](c){$\prob[N_1']\prob[N_2']$};
            \draw (2*\hs, 4*\vs) node[](ac){$N_1' \ancestralindep N_2'$};
            \draw (2*\hs, 4*\vs + 0.5*\vs) node[]{$N_1' \cup N_2' = N$};
            \draw (4*\hs, 2*\vs) node[](cd){$N_1', N_2' \in \Inj[\graph]{\graph'}$};
            \draw (4*\hs, 0*\vs) node[](d){$\prob[N_1]\prob[N_2]$};
            \draw (0, 0) node[](b){??};
            \draw[thick, ] (a) -- (ab);
            \draw[thick, ] (c) -- (cd);
            \draw[thick, ] (a) -- (ac);
            \draw[thick, ->] (ac) -- (c);
            \draw[thick, ->] (ab) -- (b);
            \draw[thick, ->] (cd) -- (d);
            \draw[very thick, red]
            (+ \cross, 1*\vs + \cross) -- (- \cross, 1*\vs - \cross)
            (+ \cross, 1*\vs - \cross) -- (- \cross, 1*\vs + \cross)
            ;
        \end{tikzpicture}
    \end{center}
    \begin{itemize}
        \item \textbf{Polynomial inequality} for $\graph$!
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pre-injectable Sets [Optional]}
    \begin{itemize}
        \item $d$-separation relations $+$ inflation $=$ polynomial inequalities over $\graph$
        \item Restrict focus to sets $N'$ that are partitioned into $N_1', N_2'$ $d$-separated by empty set $\emptyset$
        \item A \term{pre-injectable set} $N'$:
        \[ N' = {\coprod}_i N_i' \quad \forall i: N_i' \in \Inj[\graph]{\graph'} \]
        \[ \forall i, j : N_i' \ancestralindep N_j' \iff \An[\graph']{N'_i} \cap \An[\graph']{N'_j} = \emptyset \]
        \item Only need to consider \term{maximal pre-injectable sets} $\PreInj[\graph]{\graph'}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Quantum Implementation of Fritz Distribution [Optional]}
    \begin{itemize}
        \item States:
    \end{itemize}
    \begin{gather*}
        \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+}
    \end{gather*}
    \begin{itemize}
        \item Maximally entangled Bell states:
    \end{itemize}
    \[ \ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}} \quad \ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}} \]
    \begin{itemize}
        \item Measurements:
    \end{itemize}
    \begin{gather*}
        M_{A} = \bc{\ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}} \\
        M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
        M_{C} = \bc{\ket{01}\bra{01}, \ket{11}\bra{11}, \ket{00}\bra{00}, \ket{10}\bra{10}}
    \end{gather*}
    \begin{itemize}
        \item Shorthand: $\ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}}$
    \end{itemize}
\end{frame}
